---
title: "Lab 6"
author: "Gaines"
date: "11/14/2021"
output: html_document
---
**1. Write a function that conducts a randomization test for the mean difference between two groups, and show that it works. Specifically, using your function, conduct a randomization test on the same data we used in the above example from lab. Report the results and briefly discuss what the results of the randomization tell you. (6 points).**

*Inputs:
the inputs should include:
-vector for group 1
-vector for group 2
-the number of permutations/re-samplings of the data to create.

Outputs:
-output each group mean, and the difference between group means
-output a histogram of the sampling distribution of the possible mean differences produced by the randomization process 
-output the probability or odds of obtaining the observed mean difference or larger.

Optional:
-include the ability to calculate the probability of obtaining any mean difference or larger
-deal with negative difference scores appropriately
-add one or two-tailed test options*

I'm going to recreate the various steps before writing a function.

##Load in Data
```{r}
RandomTestData <- read.csv("Downloads/open_data/SchroederEpley2015data.csv", header = TRUE)
RandomTestData

#Detect Difference of Interest
RandomTestData %>% 
  group_by(CONDITION) %>%
  summarize(group_means = mean(Intellect_Rating))
```

```{r}

```

```{r}
#Set Up A Single Simulation Where Score Is Truly Random By Condition
RandomizedRandomTestData <- RandomTestData %>%
  select(CONDITION,Intellect_Rating)
RandomizedRandomTestData %>%
  mutate(Intellect_Rating = sample(Intellect_Rating))
# permute the data monte carlo style, calculating many potential new mean differences
montecarlo_potential_differences_in_rating <-c()
for(i in 1:10000){
  PermuttedRandomized_data <- RandomizedRandomTestData %>%
    mutate(Intellect_Rating = sample(Intellect_Rating)) %>%
    group_by(CONDITION) %>%
    summarize(new_means = mean(Intellect_Rating), .groups='drop')
  
montecarlo_potential_differences_in_rating[i] <-  (PermuttedRandomized_data[ PermuttedRandomized_data$CONDITION == 1,]$new_means-PermuttedRandomized_data[ PermuttedRandomized_data$CONDITION == 0,]$new_means)
}
montecarlo_potential_differences_in_rating
```

##Likelihood of getting observed score? (1-tailed)

```{r}
length(montecarlo_potential_differences_in_rating[montecarlo_potential_differences_in_rating >= 2])/length(montecarlo_potential_differences_in_rating)
```

##Likelihood of getting observed score (2-tailed)

```{r}
(length(montecarlo_potential_differences_in_rating[montecarlo_potential_differences_in_rating >= 2])+length(montecarlo_potential_differences_in_rating[montecarlo_potential_differences_in_rating <= -2]))/length(montecarlo_potential_differences_in_rating)
```

##Lets solve this with what we have before we try to put together something with upstream inputs

**1a. Extra: if the observed mean difference in the experiment was found to be .5, what would you have concluded from the randomization test?**

```{r}
print("One-Tailed:")
length(montecarlo_potential_differences_in_rating[montecarlo_potential_differences_in_rating >= .5])/length(montecarlo_potential_differences_in_rating)
print("Two-Tailed:")
(length(montecarlo_potential_differences_in_rating[montecarlo_potential_differences_in_rating >= .5])+length(montecarlo_potential_differences_in_rating[montecarlo_potential_differences_in_rating <= -.5]))/length(montecarlo_potential_differences_in_rating)
```

Regardless of tails used, I would fail to reject the null hypothesis if the real-world observed difference was .5 (h0= difference between groups is due to chance alone).

##Now to put it together and build a function
```{R}


```